Verifying Demonstrations

### 2017-08-01 abstract.tex
Removes "In this talk" line from abstract
Adapts abstract and title to Sébastien's comments

Alice organizes a protest for some change in government.
The protest is held in some location(s).
Alice wants to estimate the number of participants to prove certain support for
her change.
Current methods have wide margins for error.
In addition, Alice's incentive is to estimate the number of participants as 
high as possible whereas the government's incentive is to estimate the number 
of participants as low as possible.

We are interested in combining location proofs with electronic voting.
Since the parties' have incentives to cheat, we require transparency: we desire 
a decentralized scheme that provides the verifiability and privacy properties 
of electronic voting.
The scheme must be scalable to handle large protests.

\keywords{%
  crowd-counting; protesting; electronic voting; location proofs; privacy
}

>>>>

Say Alice organizes a protest against the current regime leader Eve.
The protest is held in some location(s) and Alice wants to estimate the number 
of participants to prove a certain support to her cause.
Current methods have wide margins for error.
In addition, Alice may be tempted to cheat by estimating the number of 
participants as high as possible whereas the government's incentive is to make 
this estimation as low as possible to support Eve.

In this work, we are interested in combining location proofs with electronic 
voting to solve this issue.
Since the parties have incentives to cheat, we require transparency: in 
particular we are aiming at a decentralized scheme that provides authenticity, 
verifiability and privacy.
More specifically, the scheme should be distributed and not depend on any 
authority.
We must also ensure that the data is time-wise related to the event (i.e.\ 
authenticity), which can be provided by blockchain-like structures.
The data must also be related to the location, something a location proof can 
achieve.
Finally, as all things policital, privacy is critical.
Similar to e-voting schemes, we need to guarantee properties close to vote 
privacy and receipt freeness --- Alice does not want Eve's agents to be able to 
infer that she is critical of Eve.
Furthermore, we need verifiability, which means that every participant can 
verify that their participation has been included --- i.e.\ individual 
verifiability, to prevent Eve from dropping data --- and that anyone
can verify the correctness of the result --- i.e.\ universal and eligibility
verifiability, to prevent any malicious actor (e.g. Sybil) from affecting the 
result.
Finally, the scheme must be scalable to handle large protests (millions of 
participants).

In this talk we will discuss this work in progress and elicit input from the 
participants.

\keywords{%
  crowd counting;
  protesting;
  electronic voting;
  location proof;
  privacy
}
